---
title: "Developmental 5 dpf screen"
output: html_document
---
packages
```{r}
library(tidyverse)
library(plotrix)
library(emmeans)
library(purrr)
library(broom)
library(forcats)
library(ggplot2)
library(rstatix)
library(tibble)
library(PMCMRplus)
library(ggnewscale)
library(devtools)
library(ggrastr)

```

```{r}
excel.names <- c("Experiment", 
                 "Treatment", 
                 "Trial", 
                 "Well",
                 "Time", 
                 "DistanceMoved", 
                 "Velocity", 
                 "Freezing_freq", 
                 "Freezing_dur", 
                 "Cruising_freq", 
                 "Cruising_dur", 
                 "Bursting_freq", 
                 "Bursting_dur", 
                 "Turn", 
                 "Ang_vel", 
                 "Meander_mean", 
                 "Meander_total")
```

upload data
```{r}
psych <- read.csv("chronic_exposure_rawdata.csv", 
                skip = 4, 
                col.names = excel.names) %>%
  mutate(Experiment = as.factor(Experiment),
          Treatment = as.factor(Treatment), 
          Trial = as.factor(Trial), 
          Well = as.factor(Well), 
         DistanceMoved = as.numeric(DistanceMoved), 
         Freezing_freq = as.numeric(Freezing_freq), 
         Cruising_freq = as.numeric(Cruising_freq), 
         Bursting_freq = as.numeric(Bursting_freq),
         Turn = as.numeric(Turn), 
         Ang_vel = as.numeric(Ang_vel), 
         Meander_mean = as.numeric(Meander_mean), 
         Meander_total = as.numeric(Meander_total))

```

Tidy the data
```{r}
#excluding frequencies in further analysis

tidymaster.forstat <- psych %>% 
  separate(col = Time, into = c("InitialTime", "FinalTime"), sep = "-") %>% #Separate initial and final times into two new columns
  mutate(InitialTime = ifelse(InitialTime == "Start", "0:00:00", InitialTime)) %>% #Reformat Start label
  separate(col = InitialTime, into = c("Hours", "Minutes", "Seconds"), sep = ":", remove = F) %>% 
  select(-Hours, -Seconds) %>% 
  mutate(Minutes = as.numeric(Minutes)) %>% 
  mutate(Label = case_when( #Label based on time ranges
    Minutes >= 10 & Minutes < 15 ~ "Light1",
    Minutes >= 15 & Minutes < 20 ~ "Dark1", 
    Minutes >= 20 & Minutes < 25 ~ "Light2",
    Minutes >= 25 & Minutes < 30 ~ "Dark2",
    Minutes >= 30 & Minutes < 35 ~ "Dark3",
    Minutes >= 35 & Minutes < 40 ~ "Dark4")) %>%
 filter(Label != is.na(Label)) %>%
 unite(newID, Experiment, Trial, Well, Label, sep = "_") %>%
 select(-InitialTime, -Minutes, -FinalTime) %>%
  mutate(Treatment = as.factor(Treatment),
         newID = as.factor(newID)) %>%
   separate(col = Treatment, into = c("Compound", "Dose"), sep =" ", remove=F) %>%
  mutate(Compound = as.factor(Compound),
         Dose = as.factor(Dose),
         Dose = fct_relevel(Dose, "Vehicle", "0.1", "0.3", "1", "10")) %>%
  separate(col = newID, into = c("T", "Trial", "Well", "Cycle"), sep = "_", remove = F) %>%
  select(-T, -Trial, -Well) %>%
  mutate(Cycle = as.factor(Cycle))
  

#How many replicates per treatment (n = x - x)

replicatecheck <- tidymaster.forstat %>%
  filter(Cycle == "Dark1") %>% 
  group_by(Treatment) %>% 
  tally()

min(replicatecheck$n) #min
max(replicatecheck$n) #max


```

Stats
```{r}
#SHAPIRO- test for normal distribution
A_shapiro <- tidymaster.forstat %>%
  gather(Variable, Value, -Treatment, -newID, -Compound, -Dose, -Cycle) %>% 
  group_by(Variable, Compound, Cycle) %>%
  nest() %>% 
   ungroup() %>% 
   mutate(shapiro = map(data, ~tidy(shapiro.test(.x$Value)))) %>%
   unnest(shapiro)
 View(A_shapiro)
#most not gaussian


#LEVENES- test for homogeneity of variances
A_levene <- tidymaster.forstat %>%
 gather(Variable, Value, -Treatment, -newID, -Compound, -Dose, -Cycle) %>% 
  group_by(Variable, Compound, Cycle) %>%
   nest() %>% 
   ungroup() %>%
   mutate(levene = map(data, ~levene_test(.x, Value ~ Treatment))) %>% 
   unnest(levene)
  View(A_levene)
#mostly not homogeneous

#KRUSKAL WALLIS - non-parametric ANOVA
A_KRUSKAL <- tidymaster.forstat %>%
  gather(Variable, Value, -Treatment, -newID, -Compound, -Dose, -Cycle) %>% 
  group_by(Variable, Compound, Cycle) %>%
  nest() %>% 
  ungroup() %>% 
  mutate(kruskal = map(data, ~kruskal_test(.x, Value ~ Treatment))) %>% 
  unnest(kruskal) 
View(A_KRUSKAL)

#DUNNET- posthoc treatment vs control (DMSO vs treatment)
A_dunnetx <- tidymaster.forstat %>% 
  select(-newID) %>% 
  gather(Variable, Value, -Treatment, -Compound, -Dose, -Cycle) %>% 
  group_by(Variable, Compound, Cycle) %>%
  nest() %>% 
  mutate(model = map(data, ~PMCMRplus::kwManyOneDunnTest(x=.x$Value, g=.x$Dose, p.adjust.method = "holm", na.rm=T) %>%
                       toTidy())) %>% 
  unnest(model) %>% 
   mutate(significant = case_when(p.value > 0.05 ~ "ns",
                                  p.value <= 0.01 ~ "**",
                                  p.value <= 0.05 ~"*"))


# edit for exporting
A_DUNNETforprint <- A_dunnetx %>% 
  select(Compound,Cycle,group1,Variable,statistic, p.value, significant) %>% 
  ungroup()

write.csv(A_DUNNETforprint, "dunnetx_stats_5dpf.csv")

```

zscore -  these are calculated within each compound across doses and parameters
```{r}
zscore <- tidymaster.forstat %>% 
  gather(Variable, Value, -Treatment, -newID, -Compound, -Dose, -Cycle) %>% 
  group_by(Variable, Compound, Cycle) %>% 
  mutate(zscore_group = ((Value - mean(Value, na.rm = T)) / sd(Value,  na.rm = T))) %>%
  ungroup() %>% 
  mutate(Variable = as.factor(Variable))

# Means for each Treatment
zscoremean <- zscore %>%
  select(-Value) %>% 
  spread(key = Variable, value = zscore_group) %>% 
  group_by(Compound, Dose, Cycle) %>%
  summarise(MeanDistance = mean(DistanceMoved, na.rm = T),
            MeanVelocity = mean(Velocity, na.rm = T),
            FD = mean(Freezing_dur, na.rm = T),
            CD = mean(Cruising_dur, na.rm = T),
            BD = mean(Bursting_dur, na.rm = T),
            Turn = mean(Turn, na.rm = T),
            AngV = mean(Ang_vel, na.rm = T),
            Mmean = mean(Meander_mean, na.rm = T),
           Mtot = mean(Meander_total, na.rm = T)) %>%
   gather(Parameter, Value, -Compound, -Dose, -Cycle) %>%
   mutate(Parameter = as.factor(Parameter)) %>%
  ungroup()
  View(zscoremean)

#Normalize to vehicle (Treatment - Vehicle), graph these
zscore_norm <- zscoremean %>%
  group_by(Dose) %>%
  spread(key=Dose, value = Value) %>% 
  mutate(`0.1` = (`0.1` - Vehicle), #need to use back ticks here!
         `0.3` = (`0.3` - Vehicle),
         `1` = (`1` - Vehicle),
         `3` = (`3` - Vehicle),
         `10` = (`10` - Vehicle),
         Vehicle = (Vehicle - Vehicle)) %>% 
  gather(key = "Treatment", value = "Value", -Parameter, -Compound, -Cycle) %>% 
  ungroup() %>% 
  mutate(Treatment = as.factor(Treatment),
         Parameter = fct_relevel(Parameter, "MeanDistance", "MeanVelocity", "FD", "CD", "BD",
                                 "Turn", "AngV", "Mmean", "Mtot"),
         Treatment = fct_relevel(Treatment, "Vehicle", "0.1", "0.3", "1",
                                 "3", "10"))

```

Create stats dataframe to merge
```{r}

stats_formerge <- A_DUNNETforprint %>% 
  mutate(Variable = fct_recode(Variable, "MeanDistance" = "DistanceMoved",
                                  "MeanVelocity" = "Velocity",
                                  "FD" = "Freezing_dur",
                                  "CD" = "Cruising_dur",
                                  "BD" = "Bursting_dur",
                                  "Turn" = "Turn", "AngV" = "Ang_vel",
                                  "Mmean" = "Meander_mean", "Mtot" = "Meander_total")) %>%
  unite(temp, Compound, group1, Cycle, Variable, sep = "/") %>% 
  select(temp, significant) %>% 
  mutate(temp = as.factor(temp))

```

Merge stats and zscores for graphing
```{r}

psych_forgraph <- zscore_norm %>%
  filter(Treatment != "Vehicle") %>% 
  unite(temp, Compound, Treatment, Cycle, Parameter, sep = "/") %>% 
  mutate(temp = as.factor(temp)) %>%
  inner_join(stats_formerge, by = "temp") %>%
  mutate(significant = ifelse(is.na(significant), "ns", significant)) %>%
  separate(temp, into = c("Compound", "Treatment", "Cycle", "Parameter"), sep = "/") %>%
  mutate(Parameter = as.factor(Parameter),
           Parameter = fct_recode(Parameter, "Mean Distance" = "MeanDistance",
                                  "Mean Velocity" = "MeanVelocity",
                                  "Freezing Duration" = "FD",
                                  "Cruising Duration" = "CD",
                                  "Bursting Duration" = "BD",
                                  "Turn Angle" = "Turn", "Angular Velocity" = "AngV",
                                  "Mean Meander" = "Mmean", "Total Meander" = "Mtot"),
         Parameter = fct_relevel(Parameter,"Total Meander","Mean Meander","Angular Velocity","Turn Angle",
                                "Freezing Duration",
                               "Bursting Duration",
                               "Cruising Duration",
                                "Mean Velocity", "Mean Distance"),
         Compound = as.factor(Compound),
         Treatment = as.factor(Treatment),
         Cycle = as.factor(Cycle),
         Cycle = fct_relevel(Cycle, "Light1", "Dark1", "Light2", "Dark2", "Dark3", "Dark4"),
         Treatment = fct_relevel(Treatment, "0.1", "0.3", "1", "3", "10")) %>%
  mutate(Compound = fct_recode(Compound, "AMPH" = "Amphetamine",
                              "COCN" ="Cocaine",
                              "DMT" = "DMT",
                              "DOI" = "DOI",
                            "IBO"  = "Ibogaine",
                            "KET" = "Ketamine",
                              "LSD" = "LSD",
                              "MDA" = "MDA",
                              "MDMA" = "MDMA",
                              "METH" = "Methamphetamine",
                              "PSI" = "Psilocin",
                              "PSY" = "Psilocybin",
                              "SCOP" = "Scopolamine"), 
         Compound = fct_relevel(Compound, "AMPH", "MDA", "MDMA", "METH", "COCN", "LSD", "DOI", "DMT", "PSI",
                                "PSY", "IBO", "KET", "SCOP"))


```

Graph- Heatmap
```{r}
xlabel <- expression(Treatment~(mu*M))

max_abs_val <- max(abs(psych_forgraph$Value))

heatmap_all <- psych_forgraph %>%
  filter(Treatment != "Vehicle") %>% 
  ggplot(aes(x=Treatment, y=Parameter, fill=Value)) +
  geom_tile(color = "white", size = 0.5) +
  geom_text(data = filter(psych_forgraph, significant == "*"), label = "*", color = "black", fontface="bold") +
  geom_text(data = filter(psych_forgraph, significant == "**"), label = "**", color = "black", fontface="bold") +
  scale_fill_distiller(palette = "RdBu", limits = c(-max_abs_val, max_abs_val)) +
  theme_bw() +
  labs(title = "Developmental Exposure (5 dpf)",
        fill = "Z-score") +
  theme(axis.text.x = element_text(vjust= 0.6, angle = 45), 
        plot.title = element_text(size=20), 
        strip.background = element_rect(fill = "white")) + 
  xlab(label = xlabel) +
  facet_grid(Cycle ~ Compound)


ggsave("psych_heatmap_all_5dpf.pdf", plot = heatmap_all, width = 14, height = 12 , units  = 'in',
       dpi = 300, limitsize = TRUE) 

```

Subset and graph just Dark1
```{r}

Dark1_psychgraph <- psych_forgraph %>%  #filter data set for Dark1 only
  filter(Cycle == "Dark1")

max_abs_valDARK1 <- max(abs(Dark1_psychgraph$Value))

heatmap_DARK1 <- Dark1_psychgraph %>%
  filter(Treatment != "Vehicle") %>% 
  ggplot(aes(x=Treatment, y=Parameter, fill=Value)) +
  geom_tile(color = "white") +
  coord_equal()+ #This makes the tiles squares instead of rectangles
  #geom_text(data = filter(psych_forgraph, significant == "*"), label = "*", color = "black", fontface="bold") + #if you want stats on the graph use these commented lines
  #geom_text(data = filter(psych_forgraph, significant == "**"), label = "**", color = "black", fontface="bold") +
  scale_fill_distiller(palette = "RdBu", limits = c(-max_abs_valDARK1, max_abs_valDARK1)) +
  theme_bw() +
  theme(axis.text.x = element_text(vjust= 0.6, angle = 45), 
        plot.title = element_text(size=16), 
        strip.background = element_rect(fill = "white")) +
  labs(title = "Developmental Exposure (5 dpf)",
        fill = "Z-score") +
  xlab(label = xlabel) +
  facet_grid( ~ Compound)

heatmap_DARK1

ggsave("psych_heatmap_Dark1_5dpf.pdf", plot = heatmap_DARK1, width = 12, height = 6 , units  = 'in',
       dpi = 300, limitsize = TRUE)

```

Significant values graph- Dark1 only
```{r}
xlabel <- expression(Treatment~(mu*M))

significant_DARK1 <- Dark1_psychgraph %>%
  filter(Treatment != "Vehicle") %>% 
  ggplot(aes(x=Treatment, y=Parameter, fill=significant)) +
  geom_tile(color = "grey") +
  coord_equal() +
  scale_fill_manual(values = c("#CCCCFF", "#330066", "white"),
                    labels = c("p<0.05", "p<0.01", "not\nsignificant")) +
  facet_grid( ~ Compound) +
  theme_bw() +
  theme(axis.text.x = element_text(vjust= 0.6, angle = 45), 
        strip.background = element_rect(fill = "white")) +
  labs(#title = "Developmental Exposure (5 dpf)",
        fill = "Significance") +
   xlab(label = xlabel)


ggsave("psych_Dark1_5dpf_significant.pdf", plot = significant_DARK1, width = 12, height = 6 , units  = 'in',
       dpi = 300, limitsize = TRUE) 

combine plots
```{r}
combined_graph <-
  cowplot::plot_grid(heatmap_DARK1, significant_DARK1, ncol = 1, align = "v", axis = "lr")

combined_graph

ggsave("combined_chronic_5dpf.pdf", plot = combined_graph, width = 12, height = 5 , units  = 'in',
       dpi = 300, limitsize = TRUE)

```


Dot plots for supplemental
```{r}

View(tidymaster.forstat)

all_forgraph <- tidymaster.forstat %>%
  gather(Variable, Value, DistanceMoved, Velocity, Freezing_dur, Cruising_dur, Bursting_dur, Turn, Ang_vel, Meander_mean, Meander_total) %>%
  select(-Freezing_freq, -Cruising_freq, -Bursting_freq) %>%
  mutate(Variable = as.factor(Variable),
         Compound = fct_recode(Compound, "AMPH" = "Amphetamine", 
                              "COCN" ="Cocaine", 
                              "DMT" = "DMT", 
                              "DOI" = "DOI", 
                            "IBO"  = "Ibogaine",
                            "KET" = "Ketamine",
                              "LSD" = "LSD", 
                              "MDA" = "MDA", 
                              "MDMA" = "MDMA", 
                              "METH" = "Methamphetamine",
                              "PSI" = "Psilocin", 
                              "PSY" = "Psilocybin", 
                              "SCOP" = "Scopolamine"),
         Compound = fct_relevel(Compound, "AMPH", "MDA", "MDMA", "METH", "COCN", "LSD", "DOI", "DMT", "PSI",
                                "PSY", "IBO", "KET", "SCOP"),
         Dose = fct_recode(Dose, "DMSO" = "Vehicle"),
         Dose = fct_relevel(Dose, "DMSO", "0.1", "0.3", "1", "3", "10"),
         Variable = fct_recode(Variable, "Mean\nDistance\n(mm)" = "DistanceMoved", 
                                  "Mean\nVelocity\n(mm/s)" = "Velocity", 
                                  "Freezing\nDuration\n(s)" = "Freezing_dur", 
                                  "Cruising\nDuration\n(s)" = "Cruising_dur",
                                  "Bursting\nDuration\n(s)" = "Bursting_dur",
                                  "Turn Angle\n(Degree(°))" = "Turn", "Angular\nVelocity\n(°/s)" = "Ang_vel", 
                                  "Mean\nMeander\n(°/mm)" = "Meander_mean", "Total\nMeander\n(°/mm)" = "Meander_total"),
         Variable = fct_relevel(Variable, "Mean\nDistance\n(mm)", "Mean\nVelocity\n(mm/s)", "Freezing\nDuration\n(s)", 
                                "Cruising\nDuration\n(s)", "Bursting\nDuration\n(s)", "Turn Angle\n(Degree(°))", 
                                "Angular\nVelocity\n(°/s)", "Mean\nMeander\n(°/mm)","Total\nMeander\n(°/mm)"))
                                

xlabel <- expression(Treatment~(mu*M))

#LIGHT1
light1_dotplot <- all_forgraph %>% 
  filter(Cycle == "Light1") %>% 
  ggplot(aes(x=Dose, y = Value, color=Dose)) +
  geom_point_rast(na.rm = T, alpha = 0.7, raster.dpi = 100) + #Rasterizing my geompoints because they are crashing InkScape and powerpoint and I want my life back
   stat_summary(fun.data = "mean_cl_normal",
               geom = "errorbar",
               col = "black",
               width = 0.2, size = 0.5) +
  stat_summary(fun="mean", geom="point", 
               col="black", size=1) +
  facet_grid(Variable ~ Compound, scales = "free") +
  theme_bw() +
  theme(axis.text.x = element_text(vjust= 0.6, angle = 45, size = 6.5), 
        strip.text = element_text(size = 9), 
        axis.title = element_text(size = 12)) +
  xlab(label = xlabel) +
    labs(title = "Developmental Exposure (5 dpf), Light 1",
      color = xlabel)

light1_dotplot

ggsave("psych_alldot_5dpf_L1.pdf", plot = light1_dotplot, width = 12, height = 12 , units  = 'in',
       dpi = 300, limitsize = TRUE)

#DARK1
dark1_dotplot <- all_forgraph %>% 
  filter(Cycle == "Dark1") %>% 
  ggplot(aes(x=Dose, y = Value, color=Dose)) +
  geom_point_rast(na.rm = T, alpha = 0.7, raster.dpi = 100) + #Rasterizing my geompoints because they are crashing InkScape and powerpoint and I want my life back
   stat_summary(fun.data = "mean_cl_normal",
               geom = "errorbar",
               col = "black",
               width = 0.2, size = 0.5) +
  stat_summary(fun="mean", geom="point", 
               col="black", size=1) +
  facet_grid(Variable ~ Compound, scales = "free") +
  theme_bw() +
  theme(axis.text.x = element_text(vjust= 0.6, angle = 45, size = 6.5), 
        strip.text = element_text(size = 9), 
        axis.title = element_text(size = 12)) +
  xlab(label = xlabel) +
    labs(title = "Developmental Exposure (5 dpf), Dark 1",
      color = xlabel)


dark1_dotplot
ggsave("psych_alldot_5dpf_D1.pdf", plot = dark1_dotplot, width = 12, height = 12 , units  = 'in',
       dpi = 300, limitsize = TRUE)

#LIGHT2
light2_dotplot <- all_forgraph %>% 
  filter(Cycle == "Light2") %>% 
  ggplot(aes(x=Dose, y = Value, color=Dose)) +
  geom_point_rast(na.rm = T, alpha = 0.7, raster.dpi = 100) + #Rasterizing my geompoints because they are crashing InkScape and powerpoint and I want my life back
   stat_summary(fun.data = "mean_cl_normal",
               geom = "errorbar",
               col = "black",
               width = 0.2, size = 0.5) +
  stat_summary(fun="mean", geom="point", 
               col="black", size=1) +
  facet_grid(Variable ~ Compound, scales = "free") +
  theme_bw() +
  theme(axis.text.x = element_text(vjust= 0.6, angle = 45, size = 6.5), 
        strip.text = element_text(size = 9), 
        axis.title = element_text(size = 12)) +
  xlab(label = xlabel) +
    labs(title = "Developmental Exposure (5 dpf), Light 2",
      color = xlabel)


ggsave("psych_alldot_5dpf_L2.pdf", plot = light2_dotplot, width = 12, height = 12 , units  = 'in',
       dpi = 300, limitsize = TRUE)

#DARK2
dark2_dotplot <- all_forgraph %>% 
  filter(Cycle == "Dark2") %>% 
  ggplot(aes(x=Dose, y = Value, color=Dose)) +
  geom_point_rast(na.rm = T, alpha = 0.7, raster.dpi = 100) + #Rasterizing my geompoints because they are crashing InkScape and powerpoint and I want my life back
   stat_summary(fun.data = "mean_cl_normal",
               geom = "errorbar",
               col = "black",
               width = 0.2, size = 0.5) +
  stat_summary(fun="mean", geom="point", 
               col="black", size=1) +
  facet_grid(Variable ~ Compound, scales = "free") +
  theme_bw() +
  theme(axis.text.x = element_text(vjust= 0.6, angle = 45, size = 6.5), 
        strip.text = element_text(size = 9), 
        axis.title = element_text(size = 12)) +
  xlab(label = xlabel) +
    labs(title = "Developmental Exposure (5 dpf), Dark 2",
      color = xlabel)

ggsave("psych_alldot_5dpf_D2.pdf", plot = dark2_dotplot, width = 12, height = 12 , units  = 'in',
       dpi = 300, limitsize = TRUE)

#DARK3
dark3_dotplot <- all_forgraph %>% 
  filter(Cycle == "Dark3") %>% 
  ggplot(aes(x=Dose, y = Value, color=Dose)) +
  geom_point_rast(na.rm = T, alpha = 0.7, raster.dpi = 100) + #Rasterizing my geompoints because they are crashing InkScape and powerpoint and I want my life back
   stat_summary(fun.data = "mean_cl_normal",
               geom = "errorbar",
               col = "black",
               width = 0.2, size = 0.5) +
  stat_summary(fun="mean", geom="point", 
               col="black", size=1) +
  facet_grid(Variable ~ Compound, scales = "free") +
  theme_bw() +
  theme(axis.text.x = element_text(vjust= 0.6, angle = 45, size = 6.5), 
        strip.text = element_text(size = 9), 
        axis.title = element_text(size = 12)) +
  xlab(label = xlabel) +
    labs(title = "Developmental Exposure (5 dpf), Dark 3",
      color = xlabel)
dark3_dotplot

ggsave("psych_alldot_5dpf_D3.pdf", plot = dark3_dotplot, width = 12, height = 12 , units  = 'in',
       dpi = 300, limitsize = TRUE)


#DARK4

dark4_dotplot <- all_forgraph %>% 
  filter(Cycle == "Dark4") %>% 
  ggplot(aes(x=Dose, y = Value, color=Dose)) +
  geom_point_rast(na.rm = T, alpha = 0.7, raster.dpi = 100) + #Rasterizing my geompoints because they are crashing InkScape and powerpoint and I want my life back
   stat_summary(fun.data = "mean_cl_normal",
               geom = "errorbar",
               col = "black",
               width = 0.2, size = 0.5) +
  stat_summary(fun="mean", geom="point", 
               col="black", size=1) +
  facet_grid(Variable ~ Compound, scales = "free") +
  theme_bw() +
  theme(axis.text.x = element_text(vjust= 0.6, angle = 45, size = 6.5), 
        strip.text = element_text(size = 9), 
        axis.title = element_text(size = 12)) +
  xlab(label = xlabel) +
    labs(title = "Developmental Exposure (5 dpf), Dark 4",
      color = xlabel)
dark4_dotplot

ggsave("psych_alldot_5dpf_D4.pdf", plot = dark4_dotplot, width = 12, height = 12 , units  = 'in',
       dpi = 300, limitsize = TRUE)

```

